Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-06 notes.tex
polished the overall thing, added a part on the Bethe lattice, added figures for Anderson molecule and Hubbard dimer

% !TEX TS-program = xelatex
\documentclass[12pt]{article}
\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
\usepackage[margin=0.5in,bottom=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks,pdfusetitle]{hyperref}
\renewcommand{\arraystretch}{1.9}
\setlength\delimitershortfall{-2pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

@@

The present method intends to calculate the quantities in a different fashion. We start with a SIAM (possibly with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian. At the fixed-point, assuming the couplings are much larger compared to the kinetic energy, we can approximate the Hamiltonian by a zero-mode of the kinetic energy part, which leads to a two-site Anderson molecule Hamiltonian. Such a model is exactly solvable. Armed with such a groundstate, we will then create the wavefunction of the entire Hubbard Hamiltonian by combining them according to a prescription which is guided by the symmetries of the problem. The impurity electron will be read off as an arbitrary site, \(p\), of the lattice, while the zero-mode site becomes the site that is nearest to it. There are also integrals of motion that come out of the URG, they make up the rest of the sites in the lattice. We will first demonstrate this explicitly for the Hubbard dimer. Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians, and this should hopefully be a step towards getting a general prescription for generating wavefunctions for the full lattice (not just dimers).

@@

\section{Creating General \(N-\)site Hubbard Hamiltonian from Anderson molecule}
We will follow the strategy outlined in the previous section. For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site. Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites. This is achieved by applying periodic boundary conditions on the edges of the lattice. A square 2d lattice is thus placed on a torus.

@@

The tiling can thus be actually done in terms of Hubbard dimers:

@@

@@

\section{Computing Greens functions and related quantities}

@@

where $G_H$ and $G_A$ are the Greens functions for the full Hubbard and the Hubbard dimer respectively:

@@

@@

\\\\
Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space. Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$. 

@@

@@

The matrix is of course written in momentum space. Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.

@@

The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$.

@@

Armed with the expression for the momentum space Greens function, one can compute the real space local Green's function by summing over the momenta:

@@

We now wish to calculate \(G_H(\vec r = 0, \omega)\) (hence test this expression) for the Hubbard dimer \(\left(N = 2, w = 1 \right)\). The discrete set of momenta are $0, \frac{\pi}{a}$, so

@@

		g_0 = \frac{2}{2} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00} \\

@@

		g_1 = -\frac{2}{2\times 1}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} \\

@@

Substituting these values into the expression gives

@@

@@

From the spectral representation, we have the following expression for the local Greens function at the $i^\text{th}$:

@@

	G_{i i}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}

@@

	G_{i i}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\

@@

The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
\begin{equation}\begin{aligned}
	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
\end{aligned}\end{equation}
The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
\begin{equation}\begin{aligned}
	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \mp t
\end{aligned}\end{equation}
for the first inner product, and
\begin{equation}\begin{aligned}
	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \pm t
\end{aligned}\end{equation}
for the second. The Greens function is therefore
\begin{equation}\begin{aligned}
	\label{dimer_local_G}
	G_{i i}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2}
\end{aligned}\end{equation}
The site local spectral can now be calculated:
\begin{equation}\begin{aligned}
	A(i\uparrow, \omega) &= - \frac{1}{\pi}\text{Im }G_{i i}^\uparrow(\omega)\\
			     &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right] + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]
\end{aligned}\end{equation}

\section*{Appendix: Greens functions for Anderson molecule}

@@

	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\

@@

We proceed exactly as before. With the following shorthand notations,

@@

	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1

@@

@@

	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\

@@

the diagonal Green's functions are

@@

	\label{mole_local_G}
	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }

@@

@@

	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }

@@

and the off-diagonal Greens functions are
	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}

>>>>

% !TEX TS-program = xelatex
\documentclass[12pt]{article}
%\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
\usepackage[margin=0.5in,bottom=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks,pdfusetitle]{hyperref}
\renewcommand{\arraystretch}{1.9}
\setlength\delimitershortfall{-2pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

@@

The present method intends to calculate the quantities in a different fashion. We start with a SIAM (possibly with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian. At the fixed-point, assuming the couplings are much larger compared to the kinetic energy, we can approximate the Hamiltonian by a zero-mode of the kinetic energy part, which leads to a two-site Anderson molecule Hamiltonian (shown in fig.~\ref{and_mol}). Such a model is exactly solvable. Armed with such a groundstate, we will then create the wavefunction of the entire Hubbard Hamiltonian by combining them according to a prescription which is guided by the symmetries of the problem. The impurity electron will be read off as an arbitrary site, \(p\), of the lattice, while the zero-mode site becomes the site that is nearest to it. There are also integrals of motion that come out of the URG, they make up the rest of the sites in the lattice. We will first demonstrate this explicitly for the Hubbard dimer. Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians, and this should hopefully be a step towards getting a general prescription for generating wavefunctions for the full lattice (not just dimers).

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.6\textwidth]{./gen_siam.png}
	\caption{Anderson molecule schematic version. It consists of two sites, impurity(blue) and zero mode(green). The impurity site has onsite repulsion, and their is inter-site hopping.}
	\label{and_mol}
\end{figure}

@@

\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers: tiling the lattice with Anderson molecules}
We will follow the strategy outlined in the previous section. For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site. Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites. This is achieved by applying periodic boundary conditions on the edges of the lattice. A square 2d lattice is thus placed on a torus.

@@

The tiling can thus be actually done in terms of Hubbard dimers (shown in fig.~\ref{hubb-dim}):

@@

	\includegraphics[width=0.6\textwidth]{./hubb_dim.png}
	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
	\label{hubb-dim}

@@

\section{Computing single particle Greens functions and related quantities}

@@

where $G_H$ and $G_D$ are the Greens functions for the full Hubbard and the Hubbard dimer respectively:

@@

\label{nn_gf}

@@

Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space. Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$. Furthermore, all expressions below are for a particular spin $\sigma$; from the spin rotational symmetry of the Hubbard Hamiltonian, the same expressions are obtained for the opposite spin.

@@

On a 2D square lattice, for instance, we obtain
\begin{eqnarray}
\xi_{\vec{q}} &=& 2(\cos q_{x}a_{x} + \cos q_{y}a_{y})\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
\epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~.\label{2dsquaretb}
\end{eqnarray}

@@

The matrix is of course written in momentum space, and diagonal. Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
\begin{eqnarray}
\Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
&=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k} = \sum_{\vec k=\vec k_1}^{\vec k_N} \Sigma_{H} (\vec{k},\omega) \ket{\vec k}\bra{\vec k}~,\nonumber\\
\Sigma_{H} (\vec{k},\omega) &=& \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
\end{eqnarray}
Thus, we can use eqs.\eqref{2dsquaretb},\eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
\par\noindent
Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.

@@

The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$

@@

The real-space Greens function, $G_{H}(\vec{r},\omega)$, can now be obtained by Fourier transforming $G_H(\vec k, \omega)$ 
\begin{equation}
G_H(\vec r, \omega) = \frac{1}{N}\sum_{\vec k} e^{i\vec{k}.\vec{r}}G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}~.
\end{equation}
Thus, we can now compute the real space local Green's function $G_H(\vec r = 0, \omega)$ by summing over the momenta:

@@

We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
\begin{eqnarray}
A_{H}(\vec{k},\omega) &=& -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[ (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right]~,\nonumber\\
A_{H}(\vec{r}=0,\omega) &=& -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = ~-\frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)~.
\end{eqnarray}
We can again use eqs.\eqref{2dsquaretb},\eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
\par\noindent
The simplest test involves calculating \(G_H(\vec r = 0, \omega)\) for the Hubbard dimer \(\left(N = 2, w = 1 \right)\). The discrete set of momenta are $0, \frac{\pi}{a}$, so

@@

		g_0\equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00} \\

@@

		g_1\equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} \\

@@

Using the expressions for $(G_{D})_{00}$ and $(G_{D})_{01}$ shown in the appendix, we can obtain $g_{0}$ and $g_{1}$ very generally. For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain

@@

\par\noindent
Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality). Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite. This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well. Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements). We can also see this from eqs.\eqref{local_gf},\eqref{nn_gf} where $(G^{H})^{-1}$ matrix has no $k$ dependence as $(G^{H})^{-1}_{ij}\propto 1/w \to 0$ as $w\to\infty$. Thus, in the self-energy 
\begin{eqnarray}
\Sigma_{H} (\vec{k},\omega) &=& \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}\nonumber\\
&\to & \lim_{w\to\infty} \omega - {g}_{0} + t^{H}\xi_{\vec{k}}~,
\end{eqnarray}
We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
\par\noindent
While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well. We will provide these expressions at a later point in time. 

@@

From the spectral representation, we have the following expression for the local Greens function for the Hubbard dimer at site $0$:

@@

	G_{D,00}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}

@@

	G_{D,00}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\

@@

The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,

@@

	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\

@@

The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore

@@

	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \mp t

@@

for the first inner product, and

@@

	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \pm t

@@

for the second. The Greens function is therefore

@@

	\label{dimer_local_G}
	G_{D,00}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2} = G_{D,00}^\downarrow(\omega, T \to 0)~.

@@

In the atomic limit $(t=0)$, the Greens function simplifies to

@@

	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{\omega}{\omega^2 - \frac{1}{4}U^2}

@@

The site local spectral function can now be calculated:
\begin{eqnarray}
A(0\uparrow, \omega) &=& - \frac{1}{\pi}\text{Im }G_{D,00}^\uparrow(\omega)\nonumber\\
			     &=& \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right]\nonumber\\ 
			     &&+ \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]\\ 
			     &=& A(0\downarrow, \omega)~.\nonumber
\end{eqnarray}
Finally, the inter-site Greens function for the Hubbard dimer is given by
\begin{equation}
\label{dimer_intersite_G}
	G_{D,01}^\uparrow(\omega, T \to 0) = \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{t}{(\omega +\frac{\Delta}{2})^2 - t^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{t}{(\omega -\frac{\Delta}{2})^2 - t^2} = G_{D,01}^\downarrow(\omega, T \to 0)~.
\end{equation}
%\section*{Appendix: Greens functions for Anderson molecule}
%\begin{equation}\begin{aligned}
%	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
%	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
%	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
%	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\
%\end{aligned}\end{equation}
%We proceed exactly as before. With the following shorthand notations,
%\begin{equation}\begin{aligned}
%	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
%	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
%	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1
%\end{aligned}\end{equation}
%\begin{equation}\begin{aligned}
%	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\
%\end{aligned}\end{equation}
%the diagonal Green's functions are
%\begin{equation}\begin{aligned}
%	\label{mole_local_G}
%	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
%				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
%\end{aligned}\end{equation}
%\begin{equation}\begin{aligned}
%	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
%				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
%\end{aligned}\end{equation}
%and the off-diagonal Greens functions are
%\begin{equation}\begin{aligned}
%	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
%				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
%G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
%\end{aligned}\end{equation}
%To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
%\begin{equation}\begin{aligned}
%	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
%	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
%	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}
%\end{aligned}\end{equation}
